Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-01 02_Paper/paper.tex
Confusion matrix

\begin{itemize}
       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project. It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
\end{itemize}

@@

Once the data is clean and compiled in one directory, the next step would be to split the data based on the assembly cycle. For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset \ref{tab:data_source}. Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so. At this point we have a series de data-samples, which each of them is based in time series. However, we are not interested in a time series analysis, therefore it would be needed to compress each time-series based data-sample in an atemporal data-sample.

@@

The robot's position at disc drop is marked in 
Figure~\ref{fig:robot_pos_cell}. The quality prediction problem is 
framed as a classification task. The input vectors which we feed into our
classifiers consists of the arm positions at the disc drops for both
discs in three dimensions, as well as the largest recorded belt speed
of all three belts. The interpretation of the quality measurement is 
used as the training target. It can be good or bad which we encode as 
zero and one.

@@

Based on the MLP prediction results presented on Table.~\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%. The false-negative results represents the 12\% of the test sample and the true predictions constitute a 88\% of the test data.

@@

Quality assurance is an important topic in production. Quality assurance methods in production might diverge one from each other, however, all of them seek to prove the product quality in one way or another.

>>>>

\begin{itemize}
       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project. It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
       \item \textbf{Conclusion}, express the remarks and diskoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
\end{itemize}

@@

Once the data is clean and compiled in one directory, the next step would be to split the data based on the assembly cycle. For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}. Subsequently, each data-sample is automatically checked for missing sensor values and diskarded if so. At this point we have a series de data-samples, which each of them is based in time series. However, we are not interested in a time series analysis, therefore it would be needed to compress each time-series based data-sample in an atemporal data-sample.

@@

The robot's position at disk drop is marked in 
Figure~\ref{fig:robot_pos_cell}. The quality prediction problem is 
framed as a classification task. The input vectors which we feed into our
classifiers consists of the arm positions at the disk drops for both
disks in three dimensions, as well as the largest recorded belt speed
of all three belts. The interpretation of the quality measurement is 
used as the training target. It can be good or bad which we encode as 
zero and one.

@@

Based on the MLP prediction results presented on Table.~\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%. The false-negative results represents the 12\% of the test sample and the true predictions constitute 88\% of the test data.

@@

% Quality assurance is an important topic in production. Quality assurance methods in production might diverge one from each other, however, all of them seek to prove the product quality in one way or another.
